---
title: "dev_history.Rmd for working package"
author: "Sébastien Rochette"
date: "23/01/2021"
output: html_document
---

```{r development, include=FALSE}
library(testthat)
```

<!--
# Description of your package

This will fill the description of your package.
Add this chunk using `fusen::description_chunk()`
--> 

```{r description}
# Describe your package
fusen::fill_description(
  fields = list(
    Title = "Manage database for GLA project",
    Description = "Create, populate and maintain a sqlite database containing all the data you need to populate a dashboard, run by the autodash package",
    `Authors@R` = c(
      person("Joe", "Heywood", email = "joe.heywood@london.gov.uk", role = c("aut", "cre"), comment = c(ORCID = "0000-0002-1565-9313")),
      person(given = "GLA", role = "cph")
    )
  ), overwrite = TRUE
)
# Define License with use_*_license()
usethis::use_mit_license("Joe Heywood")
```

# Calculate the median of a vector

```{r function}
#' Refresh the metadata 
#'
#'
#' @return
#' Logical - TRUE for worked ok
#' @export
#'
#' @examples
refresh_metadata <- function() {
  TRUE
}
```

```{r examples}
# my_median(1:12)
refresh_metadata()
```

```{r tests}
test_that("refreshing metadata works", {
})
```

# Calculate the mean of a vector
## Use sub-functions in the same chunk

```{r function-1}
#' Add data to database
#'
#' @param dat A data.frame with correct columns and at least one row
#'
#' @return
#' Logical - TRUE for worked ok.
#' @export
#'
#' @examples
insert_db <- function(x, na.rm = TRUE) {
  TRUE
}

```

```{r examples-1}
dat <- data.frame()
insert_db(dat)
```

```{r tests-1}
test_that("insert_db works properly and show error if needed", {
})
```

# There can be development actions

These will be included in the `dev_history.R` file of your package, but won't be direct part of it.

```{r development-1, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(rmd = "dev/dev_history.Rmd")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmarkdown using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory

